Road Segment Prioritization for Bicycle Infrastructure

### 2021-03-06 README.Rmd
Update PCT formula part

*OD* data can be obtained from a range of sources,
including GPS data, household travels surveys and Census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel. MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrates the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.

@@

```{=tex}
\begin{align}\label{eq:pcteqn}
     logit(C_{p}) = & -4.018 - 0.6369d +  1.988\sqrt{d} + 0.008775d^2\\ & - 0.2555s + 0.00206ds -0.1234\sqrt{d}s\nonumber 
\end{align}
```

\noindent where **d** and **s** are the distance and slope respectively
for the OD pair. The authors use square and square-root distance terms
"to capture the non-linear impact of distance on the likelihood of
cycling", and interaction terms to capture the combined effect of slope
and distance [@lovelace2017propensity]. Alternative cycling uptake
models could be used in different contexts or scenarios of change.

>>>>

*OD* data can be obtained from a range of sources,
including GPS data, household travels surveys and Census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel. MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrate the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.

@@

```{=tex}
\begin{align}\label{eq:pcteqn}
     logit(C_{p}) = & \alpha + \beta_1 d + \beta_2 \sqrt{d} + \beta_3 d^2 + \beta_4 s + \beta_5 ds + \beta_6 \sqrt{d}s\nonumber 
\end{align}
```

\noindent where **d** and **s** are the distance and slope associated with each
OD pair and $\alpha$ and $\beta$ values are parameters calculated by a regression
model on training data. The square and square-root distance terms
"capture the non-linear impact of distance on the likelihood of
cycling", and interaction terms to capture the combined effect of slope
and distance [@lovelace2017propensity]. Alternative cycling uptake
models could be 'plugged in' to our approach for different
different contexts or scenarios of change.
